\textbf{Parallel dragonfly algorithm} \\[2ex] \large High Performance Computing for Data Science course 2024/2025

### 2025-08-30 text-paper/paper.tex
updated graphics
conclusions

\begin{figure}[H]
  \includegraphics[scale=0.3]{img/speedup.jpg}
  \centering
  \caption{speedup graphic}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[scale=0.3]{img/efficiency.jpg}
  \centering
  \caption{efficiency graphic}
\end{figure}

\end{multicols}
\section{Final execution and results}
To sum up, the presented code is highly flexible and scalable, and it could be used for small optimizations on low-end systems as well as training other methods in an HPC architecture.
The code is available on GitHub, and it can be freely used in different applications.\cite{GitHub}

>>>>

\begin{figure}[H]
  \includegraphics[scale=0.5]{img/speedup.jpg}
  \centering
  \caption{Speedup graphic}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[scale=0.5]{img/efficency.jpg}
  \centering
  \caption{Efficency graphic}
\end{figure}

\end{multicols}
\section{Conclusion and final considerations}
The presented code is highly flexible and scalable, and it could be used for small optimizations on low-end systems as well as 
training other methods in an HPC architecture. There are some considerations however that need to be cited and discussed:

\begin{itemize}

\item Further analysis should be conducted in order to determine if there are better approaches that could surpass the proposed one.
As shown in the previous section OpenMP contribute does not seem fundamental for the increase of performance, suggesting a possible bottleneck
that should be optimized, peraphs considernig other technologies and parallelizing other functions than \textit{computation-accumulate}.

\item Another relevant aspect that need to be investigated is the test of fitness functions different from Rastrigin, looking at how they behave
in different situations with a HPC approach, considering also some real application in biology and engineering;
however it is pretty reasonable to assume that results should not differ too much from the ones illustrated in this paper since
Rastrigin is a hard function to optimize.
\end{itemize} The code is available on GitHub, and it can be freely 
used in different applications.\cite{GitHub}
